\documentclass{article}
\usepackage{a4wide}
\pagenumbering{gobble}

\begin{document}
  \subsection*{Lars Rohwedder}
  
    \noindent EPFL
  
    \noindent INJ 131 (Bâtiment INJ)
  
    \noindent Station 14
  
    \noindent CH-1015 Lausanne
  
  \noindent contact@larsrohwedder.com

  \noindent +41 21 693 5219

  \subsubsection*{\underline{Research Interests}}
    My research focuses mostly on algorithms in theoretical computer science. I am interested in combinatorial optimization, approximative and parameterized algorithms. Most of my work is connected to scheduling and (integer) linear programming.


  \subsubsection*{\underline{Academia}}
  
    \noindent
    Oct. 2019 - current.\textbf{ Post-Doc }- EPFL. \medskip

  
    \noindent
    Feb. 2016 - Sep. 2019.\textbf{ Ph.D. }- University of Kiel. \medskip

  
    \noindent
    Mar. 2013 - Feb. 2016.\textbf{ Master of Science (Computer Science) }- University of Kiel. \medskip

  
    \noindent
    Oct. 2010 - Feb. 2013.\textbf{ Bachelor of Science (Computer Science) }- University of Kiel. \medskip

  

  \subsubsection*{\underline{Training}}
  
    \noindent
    Apr. 2015 - Jun. 2015.\textbf{ Research Assistant }- VMWare (Palo Alto, USA). \medskip

  
    \noindent
    Feb. 2014 - Apr. 2014.\textbf{ Research Assistant }- Oracle Labs (Redwood Shores, USA). \medskip

  
    \noindent
    Mar. 2013 - Sep. 2013.\textbf{ Research Assistant }- Oracle Labs (Redwood Shores, USA). \medskip

  

  \subsubsection*{\underline{Awards and Honors}}
    I was admitted a scholarship by the Studienstiftung (German Academic Scholarship Foundation), a prestigious German organization that supports exceptionally talented students.
My Master's degree was among the three best (by grade) within the graduating class. My Bachelor's degree was the best.


  \subsubsection*{\underline{Publications}}
  
     \noindent
     Jana Cslovjecsek, Friedrich Eisenbrand, Christoph Hunkenschröder, Lars Rohwedder, Robert Weismantel. {\it Block-Structured Integer and Linear Programming in Strongly Polynomial and Near Linear Time.} manuscript. \medskip

  
     \noindent
     Moritz Buchem, Lars Rohwedder, Tjark Vredeveld, Andreas Wiese. {\it Additive Approximation Schemes for Load Balancing Problems.} manuscript. \medskip

  
     \noindent
     Etienne Bamas, Paritosh Garg, Lars Rohwedder. {\it The Combinatorial Santa Claus Problem or: How to Find Good Matchings in Non-Uniform Hypergraphs.} manuscript. \medskip

  
     \noindent
     Paritosh Garg, Sagar Kale, Lars Rohwedder, Ola Svensson. {\it Robust Algorithms under Adversarial Injections.} ICALP'20. \medskip

  
     \noindent
     Lars Rohwedder. {\it Algorithms for Integer Programming and Allocation.} Ph.D. thesis. \medskip

  
     \noindent
     Klaus Jansen, Alexandra Lassota, Lars Rohwedder. {\it Near-Linear Time Algorithm for n-fold ILPs via Color Coding.} ICALP'19. \medskip

  
     \noindent
     Klaus Jansen, Lars Rohwedder. {\it Local Search Breaks 1.75 for Graph Balancing.} ICALP'19. \medskip

  
     \noindent
     Marin Bougeret, Klaus Jansen, Michael Poss, Lars Rohwedder. {\it Approximation Results for Makespan Minimization with Budgeted Uncertainty.} WAOA'19. \medskip

  
     \noindent
     Sebastian Berndt, Leah Epstein, Klaus Jansen, Asaf Levin, Marten Maack, Lars Rohwedder. {\it Online Bin Covering with Limited Migration.} ESA'19. \medskip

  
     \noindent
     Klaus Jansen, Lars Rohwedder. {\it On Integer Programming, Discrepancy, and Convolution.} ITCS'18. \medskip

  
     \noindent
     Klaus Jansen, Lars Rohwedder. {\it A Note on the Integrality Gap of the Configuration LP for Restricted Santa Claus.} unpublished. \medskip

  
     \noindent
     Klaus Jansen, Lars Rohwedder. {\it Compact LP Relaxations for Allocation Problems.} SOSA'18. \medskip

  
     \noindent
     Klaus Jansen, Lars Rohwedder. {\it A Quasi-Polynomial Approximation for the Restricted Assignment Problem.} IPCO'17. \medskip

  
     \noindent
     Klaus Jansen, Lars Rohwedder. {\it Structured Instances of Restricted Assignment with Two Processing Times.} CALDAM'17. \medskip

  
     \noindent
     Klaus Jansen, Lars Rohwedder. {\it On the Configuration-LP of the Restricted Assignment Problem.} SODA'17. \medskip

  
\end{document}
